### 2019-03-04 README.Rmd
add singularity to dynbenchmark readme

[Docker](https://docs.docker.com/install) has to be installed to run TI methods. See https://docs.docker.com/install for instructions. For windows 10 you can install [Docker CE](https://store.docker.com/editions/community/docker-ce-desktop-windows), older Windows installations require the [Docker toolbox](https://docs.docker.com/toolbox/overview/).

@@

This command will give helpful tips if some parts of the installation are missing.

>>>>

[Docker](https://docs.docker.com/install) or [Singularity](https://www.sylabs.io/guides/3.0/user-guide/) (version ≥ 3.0) has to be installed to run TI methods. We suggest docker on Windows and MacOS, while both docker and singularity are fine when running on linux. Singularity is strongly recommended when running the method on shared computing clusters.

For windows 10 you can install [Docker CE](https://store.docker.com/editions/community/docker-ce-desktop-windows), older Windows installations require the [Docker toolbox](https://docs.docker.com/toolbox/overview/).

@@

Same for singularity:

```{r, message = TRUE, echo = TRUE}
dynwrap::test_singularity_installation(detailed = TRUE)
```

These commands will give helpful tips if some parts of the installation are missing.
